Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-10-19 prop_letter.tex
prop_letter.tex \section{Gleason} Updating...

\begin{thm}[Empty core for general QIVPMs]\label{thm:Non-extensible-of-Gleason's}In
a Hilbert space of dimension~$d\ge3$, there exists a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
such that $\coreBorn\left(\bar{\mu},\events\right)=\emptyset$.\end{thm}

@@

\begin{definition}[THOS rule]\label{def:THOS}Given a collection
of intervals $\mathscr{I}$ including $\imposs$ and $\necess$, a
function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$ is called
a THOS rule if $\iota$ is subject to the following constraints:\begin{subequations}\label{eq:iota-constraints}
\begin{eqnarray}
 &  & \iota(0)=\imposs\,,\\
 &  & \iota(1)=\necess\,,\\
 &  & \iota\left(1-x\right)=\necess-\iota\left(x\right)\,,
\end{eqnarray}
\end{subequations}and satisfies that for any three numbers~$x_{0}$,
$x_{1}$, and $x_{2}\in\left[0,1\right]$, their sum~$x_{0}+x_{1}+x_{2}\in\left[0,1\right]$
implies
\begin{equation}
\iota\left(x_{0}+x_{1}+x_{2}\right)+\iota\left(x_{2}\right)\subseteq\iota\left(x_{0}+x_{2}\right)+\iota\left(x_{1}+x_{2}\right)\,.\label{eq:iota-Inclusion}
\end{equation}
\end{definition}

\noindent Because the similarity between Def.~\ref{def:THOS} and
Def.~\ref{def:QIVPM}, $\iota\circ\mu$ should always be a IVPM no
matter in classical or quantum case. Conversely, if $\iota\circ\mu$
is always a IVPM, then $\iota$ must be a THOS rule.

\begin{thm}[The equivalence among THOS rules and IVPMs]\label{thm:iota-statements}The
following three statements are equivalent:
\begin{enumerate}
\item \label{enu:iota-subject-to}A function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
is a THOS rule.
\item \label{enu:iota-mu-CIVPM}The composited function~$\iota\circ\mu:\events_{C}\rightarrow\mathscr{I}$
is always a classical IVPM for any classical probability measure~$\mu:\events_{C}\rightarrow\left[0,1\right]$.
\item \label{enu:iota-mu-QIVPM}The composited function~$\iota\circ\mu:\events\rightarrow\mathscr{I}$
is always a QIVPM for any quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$
on any Hilbert space~$\Hilb$.
\end{enumerate}
\end{thm}

@@

\begin{thm}[A finite-precision extension of weak Gleason's theorem]\label{thm:Finite-precision-Gleason}Consider
a three-dimensional Hilbert space, and an interval-valued function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
with the maximum length of intervals $\delta$. Given any state~$\rho$,
if a state $\rho'\in\coreBorn\left(\iota\circ\mu_{\rho}^{\mathrm{B}},\events\right)$,
then the norm of their difference is $\left\Vert \rho-\rho'\right\Vert \le\delta$.\end{thm}

@@

\begin{thm}[The range of THOS rules]\label{thm:convex-uncountable}For
any THOS rule~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$, either
$\mathscr{I}=\mathscr{I}_{0}$ defined in Eq.(\ref{eq:3-value-intervals})
or $\mathscr{I}$ contains uncountably many intervals.\end{thm}

>>>>

\begin{thm}[Empty Core for General QIVPMs]\label{thm:Non-extensible-of-Gleason's}In
a Hilbert space of dimension~$d\ge3$, there exists a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
such that $\coreBorn\left(\bar{\mu},\events\right)=\emptyset$.\end{thm}

@@

\begin{definition}[THOS Rule]\label{def:THOS}Given a collection
of intervals $\mathscr{I}$ including $\imposs$ and $\necess$, a
function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$ is called
a THOS rule if $\iota$ is subject to the following constraints:\begin{subequations}\label{eq:iota-constraints}
\begin{eqnarray}
 &  & \iota(0)=\imposs\,,\\
 &  & \iota(1)=\necess\,,\\
 &  & \iota\left(1-x\right)=\necess-\iota\left(x\right)\,,
\end{eqnarray}
\end{subequations}and satisfies that for any three numbers~$x_{0}$,
$x_{1}$, and $x_{2}\in\left[0,1\right]$, their sum~$x_{0}+x_{1}+x_{2}\in\left[0,1\right]$
implies
\begin{equation}
\iota\left(x_{0}+x_{1}+x_{2}\right)+\iota\left(x_{2}\right)\subseteq\iota\left(x_{0}+x_{2}\right)+\iota\left(x_{1}+x_{2}\right)\,.\label{eq:iota-Inclusion}
\end{equation}
\end{definition}

\noindent Because of the similarity between Def.~\ref{def:THOS}
and Def.~\ref{def:QIVPM}, $\iota\circ\mu$ should always be a IVPM
no matter in classical or quantum case. Conversely, if $\iota\circ\mu$
is always a IVPM, then $\iota$ must be a THOS rule.

\begin{thm}[Equivalence among THOS Rules and IVPMs]\label{thm:iota-statements}The
following three statements are equivalent:
\begin{enumerate}
\item \label{enu:iota-subject-to}A function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
is a THOS rule.
\item \label{enu:iota-mu-CIVPM}The composited function~$\iota\circ\mu:\events_{C}\rightarrow\mathscr{I}$
is always a classical IVPM for any classical probability measure~$\mu:\events_{C}\rightarrow\left[0,1\right]$.
\item \label{enu:iota-mu-QIVPM}The composited function~$\iota\circ\mu:\events\rightarrow\mathscr{I}$
is always a QIVPM for any quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$
on any Hilbert space~$\Hilb$.
\end{enumerate}
\end{thm}

@@

\begin{thm}[Finite-Precision Extension of Weak Gleason's theorem]\label{thm:Finite-precision-Gleason}Consider
a three-dimensional Hilbert space, and an interval-valued function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
with the maximum length of intervals $\delta$. Given any state~$\rho$,
if a state $\rho'\in\coreBorn\left(\iota\circ\mu_{\rho}^{\mathrm{B}},\events\right)$,
then the norm of their difference is $\left\Vert \rho-\rho'\right\Vert \le\delta$.\end{thm}

@@

\begin{thm}[Range of THOS Rules]\label{thm:convex-uncountable}For
any THOS rule~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$, either
$\mathscr{I}=\mathscr{I}_{0}$ defined in Eq.(\ref{eq:3-value-intervals})
or $\mathscr{I}$ contains uncountably many intervals.\end{thm}
